Predicting Erectile Function in Patients Undergoing Stereotactic Body Radiation Therapy

### 2017-01-24 final_presentation.Rmd
hosmer
final commit hopefully

```{r, message=FALSE, warning=FALSE, echo = FALSE, results = "hide"}
library(readxl)
library(knitr)
library(data.table)
library(corrplot)
library(broom)
library(stargazer)
library(ggplot2)
library(gridExtra)
library(ROCR)
prostate <- read_excel("~/Downloads/Prostate SBRT Sexual Function Data.xlsx", skip = 7)
prostate <- data.table(prostate)
prostate <- prostate[complete.cases(prostate)] # remove last row which is empty
# Code ADT as numeric; Y = 1, N = 0
prostate[ADT == "Y", ADT := 1]
prostate[ADT == "N", ADT := 0]
prostate[, ADT := as.numeric(ADT)]
prostate[, centered_age := Age - mean(Age)]
prostate[`Gleason Score` <= 6, `Gleason Score` := 0]
prostate[`Gleason Score` >= 8, `Gleason Score` := 2]
prostate[`Gleason Score` == 7, `Gleason Score` := 1]
prostate[`T-Stage Group` == 2, `T-Stage Group` := 1]
```

@@

@@

## Conclusions
- Age, HRQOL, and erectile function are predictive of erectile function at two years
- HRQOL and erectile function at baseline are protective, while age is detrimental
- PSA is somewhat protective
- Younger men, with high HRQOL scores and high PSA levels, and have erectile function at baseline will likely retain their erectile function 
- HRQOL and age are the most relevant; PSA levels less so.

>>>>

```{r, message=FALSE, warning=FALSE, echo = FALSE, results = "hide"}
library(readxl)
library(knitr)
library(data.table)
library(corrplot)
library(broom)
library(stargazer)
library(ggplot2)
library(gridExtra)
library(ROCR)
library(boot)
prostate <- read_excel("~/Downloads/Prostate SBRT Sexual Function Data.xlsx", skip = 7)
prostate <- data.table(prostate)
prostate <- prostate[complete.cases(prostate)] # remove last row which is empty
# Code ADT as numeric; Y = 1, N = 0
prostate[ADT == "Y", ADT := 1]
prostate[ADT == "N", ADT := 0]
prostate[, ADT := as.numeric(ADT)]
prostate[, centered_age := Age - mean(Age)]
prostate[`Gleason Score` <= 6, `Gleason Score` := 0]
prostate[`Gleason Score` >= 8, `Gleason Score` := 2]
prostate[`Gleason Score` == 7, `Gleason Score` := 1]
prostate[`T-Stage Group` == 2, `T-Stage Group` := 1]
```

@@

## Results
- Hosmer-lemeshow test:
- X-squared value of 6.8019 
- p-value of 0.5581
- We fail to find any evidence of lack of goodness of fit
- 10-fold CV: raw estimate ~ 0.24
  - cost function: mean number incorrect at threshold = 0.5
```{r, echo = FALSE, results = "hide"}
cost <- function(r, pi = 0) {
  mean(abs(r - (pi > 0.5)))
  #cat("r:", r, "\npi:", pi, "\n")
}
mycost <- function(r, pi){
    weight1 = 1 #cost for getting 1 wrong
    weight0 = 1 #cost for getting 0 wrong
    c1 = (r==1)&(pi==0) #logical vector - true if actual 1 but predict 0
    c0 = (r==0)&(pi==1) #logical vector - true if actual 0 but predict 1
    return(mean(weight1*c1+weight0*c0))
}
cv.glm(prostate, prostate_logreg, cost, K = 10)$delta
```

@@

## Conclusions
- Age, HRQOL, and erectile function are predictive of erectile function at two years
- HRQOL and erectile function at baseline are protective, while age is detrimental
- PSA is somewhat protective
- HRQOL and age are the most relevant; PSA levels less so.

## Recommendations
- Younger men, with high HRQOL scores and high PSA levels, and have erectile function at baseline will likely retain their erectile function
```{r, echo = FALSE}
example_prostate <- prostate[c(143, 179), .(cen_age = centered_age, `Gleason Score`, T_Stage = `T-Stage Group`, PSA, HRQOL, ADT, BMI, Erec_base = `Erectile Function at Baseline`, prob_func = predicted_prob, pred_func = ifelse(predicted_prob <= 0.5, 0, 1))]
kable(example_prostate, digits = 2)
```

### 2017-01-24 paper_draft.Rmd
final commit hopefully

## Abstract
Stereotactic Body Radiation Therapy (SBRT) is a new method for treating prostate cancer. This study looks at the potential for SBRT patients to experience erectile dysfunction, an important side-effect that is associated with the treatment. Using a logistic regression model, this study finds that baseline variables including age, score on a quality of life survey, erectile function at baseline, and prostate-specific antigen levels can be used to predict the probability of having erectile function two years after recieving SBRT. The model performs well, with a value of 0.73 area under curve (AUC) and XX% predictive probability. Following the results from the model, we conclude that around XX% of patients who undergo SBRT are likely to lose erectile function.

>>>>

## Abstract
Stereotactic Body Radiation Therapy (SBRT) is a new method for treating prostate cancer. This study looks at the potential for SBRT patients to experience erectile dysfunction, an important side-effect that is associated with the treatment. Using a logistic regression model, this study finds that baseline variables including age, score on a quality of life survey, erectile function at baseline, and prostate-specific antigen levels can be used to predict the probability of having erectile function two years after recieving SBRT. The model performs well, with a value of 0.73 area under curve (AUC). Following the results from the model, we conclude that around 38 percent of patients who undergo SBRT are likely to have erectile function at two years, compared to 49 percent at baseline.
